### 2021-01-06 paper/localpsf.tex
trying to clarify dirac comb discussion

After discretization (see Appendix \ref{app:discretized_operations}), the operator $\mathcal{A}$ becomes a dense matrix, $\mathbf{A}$, that is typically too large to be built and stored. The first property is called ``matrix-free'' because at the discrete level it means that we can perform matrix-vector products of $\mathbf{A}$ and $\mathbf{A}^T$ with arbitrary vectors, but cannot easily access matrix entries $\mathbf{A}_{ij}$. In the matrix-free regime, to compute $\mathbf{A}_{ij}$ one could compute $\mathbf{v} = \mathbf{A}\mathbf{e}_j$, then extract the $i^\text{th}$ entry, $\mathbf{A}_{ij} = \mathbf{v}_i$. However, this process is wasteful because one computes the entire vector $\mathbf{v}$, then discards all but one component. Here $\mathbf{e}_j=(0,\dots,0,1,0,\dots,0)$ is the unit vector which has $j^\text{th}$ component equal to one and all other components equal to zero. In PDE constrained optimization and inverse problems, Hessians are typically available matrix free; we do not have direct access to these operators, but we can apply them to vectors via a process that involve solving two PDEs \cite{HESSIANADJOINT}. More generally, an operator is matrix-free if the process of applying the operator to a function involves solving a large linear system, using a timestepping procedure, or performing an iterative process.

@@

We compute one ``batch'' of $\varphi_i$'s by applying $\mathcal{A}$ to a sum of point sources, $\delta_{x_i},$ at many points $x_i$ (a ``Dirac comb''). That is, we compute
\begin{equation}
\label{eq:eta_intro}
	\eta := \sum_{i=1}^m A(~\cdot~, x_i) = \left\langle \mathcal{A}, \sum_{i=1}^m \delta_{x_i} \right\rangle^*.
\end{equation}
Here $\sum_{i=1}^m \delta_{x_i}$ is the Dirac comb distribution, $\left\langle \mathcal{A}, \sum_{i=1}^m \delta_{x_i} \right\rangle$ denotes the application of $\mathcal{A}$ to the Dirac comb, and $\left\langle \mathcal{A}, \sum_{i=1}^m \delta_{x_i} \right\rangle^*$ denotes the Riesz representation of the application of $\mathcal{A}$ to the Dirac comb. Although the domain of $\mathcal{A}$ is defined as $L^2(\Omega)$, which does not contain the Dirac comb distribution, the action of $\mathcal{A}$ may be extended to distributions in a natural way, as described in Appendix \ref{app:distributions}. We write $\langle \mathcal{A}, \xi \rangle$ to denote the application of $\mathcal{A}$ to the distribution $\xi$. Because $\mathcal{A}$ maps $L^2(\Omega) \rightarrow L^2(\Omega)'$, applying $\mathcal{A}$ to a function or distribution results in a linear functional. We take the Riesz representative of the linear functional $\left\langle \mathcal{A}, \sum_{i=1}^m \delta_{x_i} \right\rangle \in L^2(\Omega)'$ to convert it into a function $\left\langle \mathcal{A}, \sum_{i=1}^m \delta_{x_i} \right\rangle^* \in L^2(\Omega)$.  In computations, the process of applying $\mathcal{A}$ to the Dirac comb, then forming the Riesz representative, amounts to computing $\boldsymbol{\eta} = \mathbf{M}^{-1}\mathbf{A} \mathbf{M}^{-1} \left(\sum_{i=1}^m \boldsymbol{\delta}_{x_i}\right)$, where $\boldsymbol{\eta}$, $\mathbf{A}$, and $\boldsymbol{\delta}_{x_i}$ are discretized versions of $\eta$, $A$, and $\delta_{x_i}$, respectively, and $\mathbf{M}$ is a mass matrix.

The batch of points $x_i$ are chosen so that the support of $\left\langle \mathcal{A}, \delta_{x_i}\right\rangle^*$ and the support of $\left\langle \mathcal{A}, \delta_{x_j}\right\rangle^*$ do not overlap (or do not overlap much) if $i \neq j$. Since the impulse responses do not overlap, we may post-process $\eta$ to recover $\varphi_i$ for all of the points $x_i$ in the batch---by applying $\mathcal{A}$ to one distribution, we recover many $\varphi_i$. This is illustrated in Figure FIG. The process is repeated to get more batches of $\varphi_i$'s, until a desired number of batches is reached.

>>>>

After discretization (see Appendix \ref{app:discretized_operations}), the operator $\mathcal{A}$ becomes a dense matrix, $\mathbf{A}$, that is typically too large to be built and stored. The first property is called ``matrix-free'' because at the discrete level it means that one can perform matrix-vector products of $\mathbf{A}$ and $\mathbf{A}^T$ with arbitrary vectors, but one cannot easily access matrix entries $\mathbf{A}_{ij}$. In the matrix-free regime, to compute $\mathbf{A}_{ij}$ one could compute $\mathbf{v} = \mathbf{A}\mathbf{e}_j$, then extract the $i^\text{th}$ entry, $\mathbf{A}_{ij} = \mathbf{v}_i$. However, this process is wasteful because one computes the entire vector $\mathbf{v}$, then discards all but one component. Here $\mathbf{e}_j=(0,\dots,0,1,0,\dots,0)$ is the unit vector which has $j^\text{th}$ component equal to one and all other components equal to zero. In PDE constrained optimization and inverse problems, Hessians are typically available matrix free; we do not have direct access to these operators, but we can apply them to vectors via a process that involve solving two PDEs \cite{HESSIANADJOINT}. More broadly, $\mathbf{A}$ is matrix-free if $\mathbf{A}$ is defined implicitly via its action on vectors, and the process of applying $\mathbf{A}$ to a vector requires performing a nontrivial computational procedure, such as solving a large linear system, or timestepping.

@@

We compute one ``batch'' of $\varphi_i$'s by applying $\mathcal{A}$ to a sum of point sources, 
\begin{equation*}
	\xi := \sum_{i=1}^l \delta_{x_i},
\end{equation*}
where the $\delta_{x_i}$'s are point sources (delta distributions) centered at a collection of scattered points $x_i$. That is, we compute
\begin{equation}
\label{eq:eta_intro}
	\eta := \left\langle \mathcal{A}, \xi \right\rangle^* = \sum_{i=1}^l A(~\cdot~, x_i).
\end{equation}
Here $\left\langle \mathcal{A}, \xi \right\rangle$ denotes the result of applying the operator $\mathcal{A}$ to the distribution $\xi$, and $\left\langle \mathcal{A}, \xi \right\rangle^*$ denotes the Riesz representation of $\langle\mathcal{A}, \xi\rangle$. The distribution $\xi$ is called a \emph{Dirac comb}. Although the domain of $\mathcal{A}$ is defined as $L^2(\Omega)$, which does not contain the Dirac comb distribution, the action of $\mathcal{A}$ is extended to distributions in a natural way, as described in Appendix \ref{app:distributions}. We take the Riesz representative of the linear functional $\left\langle \mathcal{A}, \xi \right\rangle \in L^2(\Omega)'$ to convert it into a function $\left\langle \mathcal{A}, \xi \right\rangle^* \in L^2(\Omega)$.  
In computations, the process of applying $\mathcal{A}$ to the Dirac comb, then forming the Riesz representative, amounts to computing $\boldsymbol{\eta} = \mathbf{M}^{-1}\mathbf{A} \mathbf{M}^{-1} \left(\sum_{i=1}^m \boldsymbol{\delta}_{x_i}\right)$, where $\boldsymbol{\eta}$, $\mathbf{A}$, and $\boldsymbol{\delta}_{x_i}$ are discretized versions of $\eta$, $A$, and $\delta_{x_i}$, respectively, and $\mathbf{M}$ is a mass matrix.

The batch of points $x_i$ are chosen so that the support of $\left\langle \mathcal{A}, \delta_{x_i}\right\rangle^*$ and the support of $\left\langle \mathcal{A}, \delta_{x_j}\right\rangle^*$ do not overlap (or do not overlap much) if $i \neq j$. Since these supports do not overlap, we may post-process $\eta$ to recover $\varphi_i$ for all of the points $x_i$ in the batch---by applying $\mathcal{A}$ to one distribution, we recover many $\varphi_i$. This is illustrated in Figure FIG. The process is repeated to get more batches of $\varphi_i$'s, until a desired number of batches is reached.
